Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
polished up to sec 6

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\begin{figure*}[!hHtbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
	Star formation history of \flower (top right) and
	projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:virial}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their velocity dispersions are comparable to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
along the locus of $\sigma\propto R^{0.56}$.
Such high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. 
As shown in \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
%We note that previous studies by 
%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.
In fact, based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales.
On the other hand, the MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
Given the low virial parameter
and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
these structures are likely collapsing structures.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show the locii along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{P/\textrm{K cm}^{-3} = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

@@

\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$200\,\kms (see \Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results is therefore robust, haha.

@@

Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 by adopting the lowest and the highest $n_{\rm cut}$ studied here.
The uncertainties are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
This difference in slopes suggest that mo, albeit speculative due to resolution effects.
In particular, it is possible that we may identify more substructures/smaller and less massive MCs if our simulation 
was of higher resolution (but one must acknowledge that ..... is expeneisve to do zoom-in. This is what we have at best at the 
moment with simulation power).
That said, simularly massive moleuclar clouds have been reported in simulations of higher resolution (i.e., not zoom-in; \citealt{}).
It is therefore conceivable that our results are not that far off.

% interpretation
A higher $\sigma$ and $\Sigma_{\rm gas}$ is related to the higher
pressure. The higher $\Sigma_{\rm gas}$ is also related to more massive clouds being formed.
In M64, there are few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun, such massive molecular
structures are unknown to local group, and are likely the ... from which massive clusters or OB associations are to be formed.
In CMZ, we have seen molecular clouds with high pressures $P/k_B > $10$^7$\,K\,cm$^{-3}$. % also, seen in massive star-forming regions, such as 30 Doradus.

% a bit on caveat
While our result, of particular relevance here is the slope of the CMF, is subject
to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is
we are likely biased to finding more massive clouds.
High resolution simulations will be useful to shed light on
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR; however, they are more expensive to run.
On the contrary, an advantage of using cosmological zoom-in simulations for this study
is that our computational boxes are not closed, allowing us to examine how
the molecular complexes' properties vary under the influence of gas inflow/outflow 
(see e.g., \citealt{Klessen10a, Goldaum11a}). % turbulence when disk still accreting gas

@@

We quantify how stable a molecular structure is using the virial parameter, which
is defined using \Eqn{virial} and describes the balance between kinetic and gravitational potential energies.
An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note that 
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eqn{virial} 
in \Sec{PVE})}.

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
That said, our cosmological zoom-in simulation here allows us to examine 
the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldaum11a}).

>>>>

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
	Star formation history of \flower (top right) and
	projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:virial}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their velocity dispersions are comparable to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
along the locus of $\sigma\propto R^{0.56}$.
Such high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding
to the top panels of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$\,100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
As shown in the top panel of \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
%We note that previous studies by 
%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.

% PVE
We also compare the MCs identified in our simulations to 
those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
\Fig{alpha16}). The V-shaped dashed lines in the figure show the locii along which the given external pressures are needed for 
MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).

The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation. 
In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

The MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
In addition, the MCs in the satellite galaxies follow the locus of 
$\log{(P/\textrm{K cm}^{-3})}$\eq6 (see bottom panel of \Fig{alpha16}). 
Given the low virial parameter and the $\sigma^2/R - \Sigma$ relation found for these MCs in the satellite galaxies, 
these structures are likely collapsing structures.
This paints a picture, in which \SF continues as gas from the satellite galaxies are being accreted onto the main galaxies during the EoR.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show the locii along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

Similar MC properties in relation to those observed in the nearby Universe are found for \flower in its starburst phase (see bottom 
panel of \Fig{larsons_single} and \Fig{alpha27}).

@@

\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$\,200\,\kms (see \Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results is therefore robust, haha.

@@

Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 by adopting the lowest and the highest $n_{\rm cut}$ studied here.
The uncertainties are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
This suggests that the MCs of \flower are more massive compared to those observed in the nearby Universe.

% interpretation
Velocity dispersion and surface density are tightly connected to pressure. 
That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and 
since $P\propto\Sigma^2$).
In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of 
$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
from which massive star clusters or OB associations are to be formed.

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more and less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
in closed box simulations; \citealt{}).
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to gunderstand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow.
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

@@

We quantify how stable a molecular structure is using the virial parameter, which
is defined using \Eq{virial} and describes the balance between kinetic and gravitational potential energies.
An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note that 
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial} 
in \Sec{PVE})}.

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
That said, our cosmological zoom-in simulation here allows us to examine 
the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).
